Union and intersection contracts are hard, actually

### 2021-06-09 paper.tex
Typo

But which semantics? We deemed the exchange law of Figure~\ref{fig:naive-impl}
as ``clearly wrong'' with respect to overloading. There is nothing wrong per se :
we could chose a semantics for intersections that validate this rule.  However,
the resulting system wouldn't capture overloading, and is arguably not very
interesting nor useful. In~\cite{KeilThiemannUnionIntersection}, the authors
argue for basing the semantics of contracts on union and intersection type
systems, which have a simple and natural definition from which the other
properties follow. This approach makes sense, and has been continued in future
works, and in particular in~\cite{RootCauseOfBlame}.

@@

Now, combining these two context as in~\ref{fig:invalid-context} gives a context
that doesn't satisfy \nickel{Num -> Num} nor \nickel{Bool -> Bool}.  According
to the semantics of~\cite{RootCauseOfBlame}, it thus doesn't satisfy \nickel{Num
-> Num @& Bool -> Bool}. Yet, our intuition tells us that this example is a
perfectly valid context for this contract: an overloaded function satisfying
both \nickel{Num -> Num} and \nickel{Bool -> Bool} can safely be applied to a
number and to a boolean in a row. And indeed, the denotational semantics given
in~\cite{KeilThiemannUnionIntersection} does accept this context as valid.

>>>>

But which semantics? We deemed the exchange law of Figure~\ref{fig:naive-impl}
as ``clearly wrong'' with respect to overloading. There is nothing wrong per se :
we could choose a semantics for intersections that validate this rule.  However,
the resulting system wouldn't capture overloading, and is arguably not very
interesting nor useful. In~\cite{KeilThiemannUnionIntersection}, the authors
argue for basing the semantics of contracts on union and intersection type
systems, which have a simple and natural definition from which the other
properties follow. This approach makes sense, and has been continued in future
works, and in particular in~\cite{RootCauseOfBlame}.

@@

Now, combining these two context as in Figure~\ref{fig:invalid-context} gives a context
that doesn't satisfy \nickel{Num -> Num} nor \nickel{Bool -> Bool}.  According
to the semantics of~\cite{RootCauseOfBlame}, it thus doesn't satisfy \nickel{Num
-> Num @& Bool -> Bool}. Yet, our intuition tells us that this example is a
perfectly valid context for this contract: an overloaded function satisfying
both \nickel{Num -> Num} and \nickel{Bool -> Bool} can safely be applied to a
number and to a boolean in a row. And indeed, the denotational semantics given
in~\cite{KeilThiemannUnionIntersection} does accept this context as valid.
